### 2014-05-06 Thesis/Latex/hfdst-sensamp.tex
schrijfsel final

\begin{table}
\begin{tabular}{|c|c|c|c|c|c|}
\hline Transistor & Parameter & Richtingscoëfficiënt [$\frac{mV}{\sigma}$] & W [nm] & L [nm] & $\sigma$ \\ 
\hline Mupbar & Vt & 22.733 & 100 & 45 & 37.2678mV \\ 
\hline Mup & Vt & -22.250 & 100 & 45 & 37.2678mV \\ 
\hline Mupbar & $\beta$ & 13.583 & 100 & 45 & 17.8885\% \\ 
\hline Mpassn & $\beta$ & 13.467 & 100 & 45 & 29.8142\% \\ 
\hline Mpassbarn & $\beta$ & -13.117 & 100 & 45 & 29.8142\% \\ 
\hline Mup & $\beta$ & -13.033 & 100 & 45 & 17.8885\% \\ 
\hline Mdownbar & $\beta$ & -9.383 & 100 & 45 & 29.8142\% \\ 
\hline Mdown & Vt & -9.267 & 100 & 45 & 42.0381mV \\ 
\hline Mdownbar & Vt & 9.233 & 100 & 45 & 42.0381mV \\ 
\hline Mdown & $\beta$ & 8.217 & 100 & 45 & 29.8142\% \\ 
\hline Mpassp & $\beta$ & -4.50 & 100 & 45 & 17.8885\% \\ 
\hline Mpassbarp & $\beta$ & 4.383 & 100 & 45 & 17.8885\% \\ 
\hline Mpassbarp & Vt & 0.70 & 100 & 45 & 37.2678mV \\ 
\hline Mpassp & Vt & -0.70 & 100 & 45 & 37.2678mV \\ 
\hline Mbottom & $\beta$ & 0.083 & 100 & 45 & 29.8142\% \\ 
\hline Mbottom & Vt & -0.033 & 100 & 45 & 42.0381mV \\ 
\hline Mpassbarn & Vt & 0 & 100 & 45 & 42.0381mV \\
\hline Mpassn & Vt & 0 & 100 & 45 & 42.0381mV \\
\hline Mtop & Vt & 0 & 100 & 45 & 37.2678mV \\
\hline Mtop & $\beta$ & 0 & 100 & 45 & 17.8885\% \\
\hline 
\hline & $\sigma_{Voffset}$: & 45.6813mV & & & \\
\hline
\end{tabular} 
\caption{Sensitiviteitsanalyse van de minimale SA}
\label{tab:min-sensanalysis}
\end{table}

>>>>

\begin{table}
\begin{tabular}{cccccc}
\hline 
Transistor & Parameter & Richtingscoëfficiënt [$\frac{mV}{\sigma}$] & W [nm] & L [nm] & $\sigma$ \\ 
\hline 
Mupbar & Vt & 22.733 & 100 & 45 & 37.2678mV \\ 
Mup & Vt & -22.250 & 100 & 45 & 37.2678mV \\ 
Mupbar & $\beta$ & 13.583 & 100 & 45 & 17.8885\% \\ 
Mpassn & $\beta$ & 13.467 & 100 & 45 & 29.8142\% \\ 
Mpassbarn & $\beta$ & -13.117 & 100 & 45 & 29.8142\% \\ 
Mup & $\beta$ & -13.033 & 100 & 45 & 17.8885\% \\ 
Mdownbar & $\beta$ & -9.383 & 100 & 45 & 29.8142\% \\ 
Mdown & Vt & -9.267 & 100 & 45 & 42.0381mV \\ 
Mdownbar & Vt & 9.233 & 100 & 45 & 42.0381mV \\ 
Mdown & $\beta$ & 8.217 & 100 & 45 & 29.8142\% \\ 
Mpassp & $\beta$ & -4.50 & 100 & 45 & 17.8885\% \\ 
Mpassbarp & $\beta$ & 4.383 & 100 & 45 & 17.8885\% \\ 
Mpassbarp & Vt & 0.70 & 100 & 45 & 37.2678mV \\ 
Mpassp & Vt & -0.70 & 100 & 45 & 37.2678mV \\ 
Mbottom & $\beta$ & 0.083 & 100 & 45 & 29.8142\% \\ 
Mbottom & Vt & -0.033 & 100 & 45 & 42.0381mV \\ 
Mpassbarn & Vt & 0 & 100 & 45 & 42.0381mV \\
Mpassn & Vt & 0 & 100 & 45 & 42.0381mV \\
Mtop & Vt & 0 & 100 & 45 & 37.2678mV \\
Mtop & $\beta$ & 0 & 100 & 45 & 17.8885\% \\
\hline 
\hline & $\sigma_{Voffset}$: & 45.6813mV & & & \\
\hline
\end{tabular} 
\caption{Sensitiviteitsanalyse van de minimale SA}
\label{tab:min-sensanalysis}
\end{table}
